R Notebook

### 2018-02-06 paper/doc/structure.tex
small corrections

In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a recurring theme. By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change. Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector. If the right to produce digital media content were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision. They also threatened to lose their competitiveness with commercial media. On the other hand, there is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees. They complain about a bias in competition caused by public media offering online text-content because of their fee financing. The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues.

@@

\begin{enumerate}
	\item \textbf{Discovering Topics} Discover latent topics in the corpus using structural topic modeling (STM)\citep{roberts_model_2016} An extension of latent dirichlet allocation (LDA) \citep{blei_latent_2003}). The STM approach models (a) topics as multinomial distributions of words and (b) documents as multinomial distributions of topics, allowing to incorporate external variables that effect both (a) topical content and (b) topical prevalence. To explore the results, we label each topic by looking at most frequent words and most representative articles across all news providers. (Section \ref{ch_model})

	\item \textbf{Measuring Similarity of news content} Different approaches to examine the similarities / differences of content between the news provider:
	\begin{enumerate}
		\item \textbf{Differences in topic prevalence:} As we allow prevalence of topics to evolve over time (by month) and vary across newswire services, we can use the posterior topic-probability of document $d$, to estimate the conditional expectation of topic prevalence $\theta_d$ for given document characteristics (lm on compositional data) \citep{roberts_model_2016}. 
		\begin{align*}
			\theta_d=\alpha+\beta_1x_{site}+\beta_2x_{month}+\epsilon
		\end{align*}

		\item \textbf{Topic correlation} How are topics linked and framed differently across news wires? Find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.

		\item \textbf{Differences in word-topic distributions} From the STM we get a $K$x$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the news provider. That is, for each news provider we get a respective $K$x$V$ matrix. We then use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence.

@@

The market for media content in Germany is characterized by the coexistence of public and private broadcasters. By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change. Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector. In 2017, 22 own websites and 100 apps were operated by public broadcasters on which they offer their content. As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news. In the following, we will briefly discuss the characteristics of the market for online news.

@@

Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention.\cite{evans_industrial_2005} The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising. Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}. Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers. Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site. In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible. In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site. Online advertising makes it possible to target ads to particular consumers in real time.

@@

On the basis of these justifications, this paper examines whether imperfections in the market of online news exist. In other words, whether socially desired content that meets the (social) needs of society and is therefore politically desirable is not provided by the market. In order to examine this, the online news content of public media is compared with the supply of private news providers. In the event that there is no market failure in terms of information provision (the contents do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted.

@@

Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de.

\begin{figure}[H]
	\caption{}
	\begin{center}
		\begin{subfigure}[normla]{0.8\textwidth}
			\includegraphics[width=\textwidth]{../figs/reach.png}
			\caption{Percentage of daily pageviews}
			\label{fig_reach}
		\end{subfigure}
	\end{center}
\end{figure}

Users can access a website either directly or through an intermediary, such as search engines or social media. As the figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by a source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers. In the case of Bild.de, the percentage is 85\%. Also n-tv.de (79\%), spiegel.de (76\%) and tagesschau.de (75\%) get most of their traffic via the direct route. Other providers are more reliant on intermediaries, mainly search engines. Focus.de, Deutschlandfunk.de, Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines. Thus, an important question is, which organic search keywords send traffic to a website. Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to handelsblatt.com come from the keyword "handelsblatt". It is not surprising that the provider's name is the keyword that generates the majority of traffic for most of the news pages. However, different topics as well as names of other providers are hidden among the top 10 keywords.

\begin{figure}[H]
	\caption{Traffic Sources}
	\begin{center}
		\includegraphics[width=0.6\textwidth]{../figs/traffic_source.png}
		\label{fig_traffic}
	\end{center}
\end{figure}

@@

We conduct our estimation on a sample of 9393 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider. The reason for this is that the content of Tagesschau.de is most similar to that of the private providers. ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews. The articles are dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started. The scraping code was written in Python and can be made available on request.} We then filtered all articles from the section "domestic policy" by checking the URL structure.

@@

\todo{Separate by ownership and explain why article distribution represents real-world.}

@@

To use text as data and reduce the dimensionality, a common strategy is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider \citep{gentzkow_text_2017}. An overview of how these steps were applied to our data set can be found in the next section.

@@

A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}. This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document. Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information.

Intuitively the term frequency (tf) of a word is a measure of how important that word may be. There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected. We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus.

\subsection{Similar Research}

M.Paul (Cross-Collection Topic Models: Automatically Comparing and Contrasting Text): compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata. They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to analyse how they discuss topics differently. Comparing the top words of the word-topic distribution, they find some content differences between the two.

@@

We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g. the author or date of a document). STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}. \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms. Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} use topic model methods in on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.

STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies and \citet{mishler_using_2015} shows that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data. Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}. \citet{mueller_reading_2016} uses newspaper text to predict armed conflicts in different regions. They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample. In order to demonstrate multi-modality of topic-models\footnote{That is, the solution of topic-models can be sensitive to the starting values as the function to be optimized has multiple modes.} can be mitigated, \citep{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S. presidential election. With the aim of revealing the effect of partisan membership on topic prevalence, each blog is assigned to be either liberal or conservative. To explore the differences between the two, they look at the expected proportion of topic and examine the posts most associated with a respective topic. This approach is similar to \citet{roberts_model_2016}. They also use different measures of distance between the topic-word distributions of the same topic within different models. In section \ref{ch_similarity}, we apply a similar approach to measure similarity between the same topic for different covariate levels.

@@

Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}. Topic models are usually imprecise as the function we are optimizing has multiple modes, such that the model results can be sensitive to the starting values. Since an ex ante valuation of a model is hardly possible, we compute a variety of different models and compare their posterior probability. This enables us to check how substantively different results are for different model solution \citep{roberts_navigating_2016}. We then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}. We apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.

This process revealed that a model with 40 topics best reflects the structure in the corpus. Furthermore, we use the ownership of the news provider of each article (public or private) and the month it was published as covariates in the topic prevalence. In other words, the probability distribution of topics depends on the business-model of a media house as well as on the month the article was published. We also include ownership as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies. To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.

@@

In this section we summarize the results of the STM and apply different measures to analyze the content differences between public and private ownership.

Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus. To assign a label to each topic, we looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}. Figure \ref{fig_topic_proportion_diff} plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.

\begin{figure}[H]
	\begin{center}
	\caption{Expected topic proportion}
	\begin{subfigure}[normla]{0.4\textwidth}
		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion.png}
		\caption{Entire corpus}
		\label{fig_topic_proportion}
	\end{subfigure}

	\begin{subfigure}[normla]{0.4\textwidth}
		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion_diff.png}
		\caption{Differences}
		\label{fig_topic_proportion_diff}
	\end{subfigure}
\end{center}
\end{figure}

% ----------------------
% Effect of covariates
% ----------------------
We use various approaches to investigate the differences between news provider content: (1) First, we use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics. (2) Next, we find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different news wires, indicating how topics are connected and framed differently in each newswire. Approaches (1) and (2) have been used in \citep{roberts_model_2016} \todo{Noch 1,2,3 studien angeben ,die das gemacht haben.} However, we extend the analysis by (3) calculaing the similarity of the word-topic distribution $\beta$ between the news provider using different distance metrices, to identify which topics are discussed similar and differently.

\citep{roberts_navigating_2016}: Poliblog corpus to examine the role of partisanship in topical coverage.

\subsection{Differences in topic prevalence}
Since we included news source as a covariate in estimating topical prevalence part within the model, we can estimate the frequency a topic is discussed within a news corpus \citep{roberts_model_2016}. We estimate the conditional expectation of topic prevalence for given document characteristics. More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}). The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.

@@

Figures \ref{fig_estimateEffects1} and \ref{fig_estimateEffects2} display the regression results.

\begin{figure}[H]
	\caption{Regression results 1}
		\begin{center}
			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates_site.png}
		\end{center}
	\label{fig_estimateEffects1}
\end{figure}

\begin{figure}[H]
	\caption{Regression results 2}
		\begin{center}
			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates_month.png}
		\end{center}
	\label{fig_estimateEffects2}
\end{figure}

@@

@@

Since the word distribution of a topic is a simple mapping of text in space, we can use their word distribution $\beta$ to compute the similarity. More precisely, we get a respective $\beta$, $K$x$V$ matrix for each covariate level. We use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence. Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$. It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$. Let $p(x)$ and $q(x)$ be two probability density functions, the Jensen-Shannon distance $D_{js}(p,q)$ between this two distributions is defined as:

\begin{align*}
	D_{js}(p,q)=\frac{1}{2}D_{KL}(p,\frac{p+q}{2})+\frac{1}{2}D_{KL}(q,\frac{p+q}{2})
\end{align*}

where $D_{KL}$ is the Kullback-Leibler divergence between $p$ and $q$ defined as:

\begin{align*}
	D_{KL}(p,q)=\sum_{i=1}^T p_i ln \frac{p_i}{q_i}
\end{align*}

>>>>

In Germany, the debate about the role of public media and their mission in a rapidly changing media world is a recurring theme. By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change. Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector. There is the concern of commercial providers who are registering an ever-increasing number of digital services financed by fees. They complain about a bias in competition caused by public media offering online text-content because of their fee financing. The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues. However, if the right to produce digital media content were to be withdrawn from the public media outlets, they would not only be deprived of the possibility of improved information provision. They also threatened to lose their competitiveness with commercial media.

@@

\begin{enumerate}
	\item \textbf{Discovering Topics} Discover latent topics in the corpus using structural topic modeling (STM)\citep{roberts_model_2016} An extension of latent dirichlet allocation (LDA) \citep{blei_latent_2003}). The STM approach models (a) topics as multinomial distributions of words and (b) documents as multinomial distributions of topics, allowing to incorporate external variables that effect both (a) topical content and (b) topical prevalence. We will include the business model (public or private) as a control for both the topical content and the topical prevalence. Additional, we include the month an article was published as a control for the topical prevalence. To explore the results, we label each topic by looking at most frequent words and most representative articles across all news providers. (Section \ref{ch_model})

	\item \textbf{Measuring Similarity of news content} Different approaches to examine the similarities / differences of content between the news provider:
	\begin{enumerate}
		\item \textbf{Differences in topic prevalence:} As we allow prevalence of topics to evolve over time (by month) and vary across business models, we can use the posterior topic-probability of document $d$, to estimate the conditional expectation of topic prevalence $\theta_d$ for given document characteristics (lm on compositional data) \citep{roberts_model_2016}. 
		\begin{align*}
			\theta_d=\alpha+\beta_1x_{site}+\beta_2x_{month}+\epsilon
		\end{align*}

		\item \textbf{Topic correlation} To get an idea of how topics are linked and framed differently across news wires, we find all edges between topics where they exhibit a positive correlation above 0.1 \citep{roberts_model_2016}.

		\item \textbf{Differences in word-topic distributions} From the STM we get $\beta_{kv}$ - a $K$x$V$ matrix (where $K=$ number of topics and $V=$ vocabulary) of the whole corpus that contains the probability of seeing each word of the vocabulary $V$ within topic $k$ conditional on the business model (we get two different $\beta_{kv}$ for each topic $k$, as we have two specifications of the business model covariate: public and private). We then use each row (corresponding to each topic) to calculate the similarity of the word-topic distribution between the news provider using the square root of the Jensen-Shannon (JS) Divergence. We also compare this distance metric with three other measures of the similarity of distributions.

@@

The market for media content in Germany is characterized by the coexistence of public and private broadcasters. By shifting media content to the Internet, the dual system, which has been shaping the German television and radio landscape since the introduction of private broadcasting in the early 1980s, is facing a radical change. Since 2000, public broadcasting has expanded its range of services, particularly in the digital media sector. In 2017, 22 own websites and 100 apps were operated by public broadcasters on which they offer their content. As a result, public broadcasting no longer only competes with private television and radio stations, but also enters the market for online news. In the following, we will briefly discuss the characteristics of the market for online news in Germany.

@@

Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention \citep{evans_industrial_2005}. The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising. Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}. Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers. Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site. In fact, most advertising-financed online magazines earn their gross margin from advertising \citep{evans_industrial_2005}. In order to maximize their profits, these companies have an interest in attracting as many readers as possible. In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site. Online advertising makes it possible to target ads to particular consumers in real time.

@@

On the basis of these justifications, this paper examines whether imperfections in the market of online news exist. In other words, whether socially desired content that meets the (social) needs of society and is therefore politically desirable is not provided by the market. In order to examine this, the online news content of public media is compared with the supply of private news providers, by comparing the topic prevalence between them. In the event that there is no market failure in terms of information provision (the contents do not differ), the existence of public media could still be justified by the fact that socially relevant contents of private providers are systematically distorted and the existence of public offerings ensures the diversity of information and opinions transmitted. We try to examine this part by analyzing how the topics are discussed differently for public and private news provider. For this purpose, we calculate the divergence of the word probabilities of a topic.

@@

The following analysis of the online news market includes the largest suppliers of online news. Figure \ref{fig_reach} shows the largest providers of online news in terms of daily pageviews.\footnote{The figure shows the estimated percentage of daily pageviews on the internet that occurred on a specific website.} It is striking that SPIEGEL ONLINE has the greatest reach over the entire course of time followed by Bild.de. Public websites like Deutschlandfunk.de or Tagesschau.de have a rather small share in that market.

\begin{figure}[H]
			\includegraphics[width=0.8\textwidth]{../figs/reach.png}
			\caption{Percentage of daily pageviews}
			\label{fig_reach}
\end{figure}

Users can access a news website either directly or through an intermediary, such as search engines or social media. As the Figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by a source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers. In the case of Bild.de, the percentage is 85\%. Also n-tv.de (79\%), SPIEGEL ONLINE (76\%) and Tagesschau.de (75\%) get most of their traffic via the direct route. Other providers are more reliant on intermediaries, mainly search engines. FOCUS ONLINE, DLF and Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines. Thus, an important question is, which organic search keywords send traffic to a website. Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to Handelsblatt.com come from the keyword "handelsblatt". It is not surprising that the provider's name is the keyword that generates the majority of traffic for most of the news pages. However, different topics as well as names of other providers are hidden among the top 10 keywords.

\begin{figure}[H]
	\caption{Traffic Sources}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{../figs/traffic_source.png}
		\label{fig_traffic}
	\end{center}
\end{figure}

@@

We conduct our estimation on a sample of 9393 online news articles from six news provider about domestic politics\footnote{Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, ZEIT ONLINE, Tagesschau.de}, of which only Tagesschau.de belongs to the group of public provider. The reason for this is that the content structure of Tagesschau.de is most similar to that of the private providers. ZDF.de offers predominantly video content and DLF website mainly offers audio content in the form of interviews, which makes it hard to include in the model0 However, as we only include some of the above mentioned private suppliers, the proportions between private and public market participants are maintained, thus minimizing possible bias. The articles are dated from 01.06.2017 to 31.12.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles using the the Webhose.io API.\footnote{For more information see https://docs.webhose.io/v1.0/docs/getting-started. The scraping code was written in Python and can be made available on request.} We then filtered all articles from the section "domestic policy" by checking the URL structure.

@@

@@

A central task in text mining is to extract low-dimensional information from documents that are high-dimensional by nature \citep{bholat_text_2015}. This is related to the task of reducing the number of unique language elements in order to reduce the dimensionality of data (to avoid unnecessary computational complexity and overfitting) while at the same time keeping those words that reflect the content of a document. Any useful representation of text will throw away some information, the trick is to include the relevant information for our needs, and exclude the extraneous information. To use text as data and reduce the dimensionality, a common strategy is to pre-process the text by imposing some preliminary restrictions (stop-word removal, tokenization) based on the nature of the data (twitter text, newspaper articles, speeches, etc.) to reduce the number of language elements to consider \citep{gentzkow_text_2017}. Intuitively the term frequency (tf) of a word is a measure of how important that word may be. There are words in a document, however, that occur many times but may not be important like articles, conjunctions, and so on. These terms, often called "stop words", are important to the grammatical structure of a text, but typically don't add any additional meaning and can therefore be neglected. We use a pre-defined stop word list from the Snowball stemmer project\footnote{http://svn.tartarus.org/snowball/trunk/website/algorithms/*/stop.txt} together with a customized list of stop-words that are redundant superfluous or distorting. We also remove punctuation character (e.g. ., ,, !, ?, etc.) and all numbers from our corpus. After completing this steps we were left with 55.235 unique terms in our vocabulary.

@@

@@

We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g. the author or date of a document). STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}. \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms. Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} use topic model methods in on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades. \citet{paul_cross-collection_2017} compares editorial differences between media sources, using cross-collection latent Dirichlet allocation (ccLDA), an LDA-based approach that incorporates differences in document metadata. They use a dataset of 623 news articles from August 2008 from two American media outlets - msnbc.com and foxnews.com - to analyse how they discuss topics differently. Comparing the top words of the word-topic distribution, they find some content differences between the two.

STM has been applied to multiple academic fields: \citet{roberts_structural_2014} uses STM to analyse open-ended responses from surveys and experiments, \citet{farrell_corporate_2016} applies the model to scientific texts on climate change, revealing links between corporate funding and the framing of scientific studies and \citet{mishler_using_2015} shows that "STM can be used to detect significant events such as the downing of Malaysia Air Flight 17" when applied to twitter data. Another study shows how STM can be used to explore the main international development topics of countries’ annual statements in the UN General Debate and examine the country-specific drivers of international development rhetoric \citep{baturo_what_2017}. \citet{mueller_reading_2016} uses newspaper text to predict armed conflicts in different regions. They use the estimated topic shares in linear fixed effects regression to forecast conflict out-of-sample. In order to demonstrate multi-modality of topic-models\footnote{That is, the solution of topic-models can be sensitive to the starting values as the function to be optimized has multiple modes.} can be mitigated, \citet{roberts_navigating_2016} use STM to examine the role of partisanship in topical coverage using a corpus of 13,246 posts that were written for 6 political blogs during the course of the 2008 U.S. presidential election. With the aim of revealing the effect of partisan membership on topic prevalence, each blog is assigned to be either liberal or conservative. To explore the differences between the two, they look at the expected proportion of topic and examine the posts most associated with a respective topic. This approach is similar to \citet{roberts_model_2016}. They also use different measures of distance between the topic-word distributions of the same topic within different models. In section \ref{ch_similarity}, we apply a similar approach to measure similarity between the same topic for different covariate levels.

@@

Inference of mixed-membership models, such as the one applied in this paper, has been a thread of research in applied statistics in the past few years \citep{blei_latent_2003} \citep{erosheva_mixed-membership_2004} \citep{braun_variational_2010}. Topic models are usually imprecise as the function we are optimizing has multiple modes, such that the model results can be sensitive to the starting values. Since an ex ante valuation of a model is hardly possible, I compute a variety of different models and compare their posterior probability. This enables me to check how substantively different results are for different model solution \citep{roberts_navigating_2016}. I then cross-checked some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}. I apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.

This process revealed that a model with 40 topics best reflects the structure in the corpus. Furthermore, we use the ownership of the news provider of each article (public or private) and the month it was published as covariates in the topic prevalence. In other words, the probability distribution of topics depends on the business-model as well as on the month the article was published. We also include ownership as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies. To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.

@@

In this section I summarize the results of the STM and apply different measures to analyze the content differences between public and private ownership. We use various approaches to investigate the differences between news provider content: (1) To address the question whether market imperfections exist in that sense, that some topics are not covered by private but by public news provider, I use the document-topic probability $\theta$, to estimate the conditional expectation of topic prevalence for given document characteristics. (2) Next, I find all edges between topics where they exhibit a positive correlation of $\theta$ above 0.1 to examine how topics are correlated differently for different covariate levels, indicating how topics are connected and framed differently between private and public media. Approaches (1) and (2) have been used in \citep{roberts_model_2016}. However, we extend the analysis by (3) calculating the similarity of the word-topic distribution $\beta$ between the news provider using different distance measures, to identify which topics are discussed similar or differently. This process also helps us to understand whether the supply of public media

Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure). Thus topics more associated with public media appear to the right of zero. To assign a label to each topic, we looked at the most frequent words in that topic and the most representative articles \citep{roberts_model_2016}.

\begin{figure}[H]
	\begin{center}
	\caption{Expected topic proportion}
		\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic_proportion.png}
		\caption{Expected topic proportions}
		\label{fig_topic_proportion}
\end{center}
\end{figure}

\textcolor{red}{AUSWERTUNG}

\subsection{Differences in topic prevalence}
Since we included news source as a covariate in estimating topical prevalence part within the model, we can estimate the frequency a topic is discussed within a news corpus \citep{roberts_model_2016}. We estimate the conditional expectation of topic prevalence for given document characteristics. More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents (see equation \ref{eq_1}). The stm-package provides a function that uses the method of composition to incorporate uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results \citep{roberts_stm:_2016}.

@@

Figure \ref{fig_estimateEffects} display the regression results for private vs. public. As we also control for the month, the intercept gives the mean of private news suppliers in June 2017.\footnote{Table of regression results can be found in appendix.}

\begin{figure}[H]
	\caption{Regression results}
		\begin{center}
			\includegraphics[width=0.9\textwidth,keepaspectratio]{../figs/estimates_site.png}
		\end{center}
	\label{fig_estimateEffects}
\end{figure}

\textcolor{red}{AUSWERTUNG}

@@

\textcolor{red}{AUSWERTUNG}

@@

Since a topic is a multinomial distribution over the vocabulary, where $\beta_{kvi}$ indicates the probability of observing word $v$ in topic $k$ for covariate level $i$, we can analyze how similar a topic $k$ is for different levels of covariates. More precisely, we can calculate the similarity between $\beta_{kvi}$ and $\beta_{kvj}$. I use each row of that matrix (corresponding to each topic) to calculate the similarity of the word-topic distribution between the public and private media using the square root of the Jensen-Shannon (JS) Divergence. I will compare this metric with a set of other similarity measures recently used in the literature to measure the difference between word-topic distributions: The Kullback-Leibler (KL) divergence (\citet{newman_distributed_2009}, \citet{wang_mining_2009}), the cosine similarity (\citet{he_detecting_2009}, \citet{ramage_labeled_2009}) and the difference of the $L1$ norm of the vectors \citep{roberts_navigating_2016}. I will briefly explain these measures before I proceed to the results.

Essentially, what we're looking at with the KL divergence is the expectation of the log difference between probabilities $a$ and $b$. It can be defined as:

\begin{align*}
	D_{KL}(a,b)=\sum_{i=1}^T a_i \text{ln} \frac{a_i}{b_i}
\end{align*}

So $D_{kl} \to 0$ indicates stronger similarities. However, since the KL divergence is not symmetric, it cannot be used to measure the distance between two distributions, but as a divergence measure.
